Methods with preconditioning with weight decay regularization

### 2023-03-08 paper/main.tex
update title
add experiment

\title{A template for the \emph{arxiv} style}

\author{ Kreinin M. \\
	Department of Intelligent Systems\\
	MIPT\\
	Moscow, Russia \\
	\texttt{kreinin.mv@phystech.edu} \\
}
\date{}

@@

\keywords{Adam \and OASIS \and Regularization \and ADAHessian}

@@

For solving these problems we always scaled adaptive gradients algorithms like ADAM, OASIS, ADAHessian. We investigate how the convergence rate will change when the regularization function is added to these algorithms.
\if 0
\begin{algorithm}[H]
	\caption{Based algorithm}\label{alg:Based}
	$w_0, D_0, \eta_0$
	\begin{algorithmic}
		\For{$k = 1, 2, ...$}
		\State $D_k$ - update
		\State $\eta_k$ - update
		\State Set $w_{k+1} = w_k - \eta_k D_k^{-1} \nabla F(w_k)$
		\EndFor
	\end{algorithmic}
\end{algorithm}
\fi

\if 0
Examples of similars algorithms.
\begin{algorithm}[H]
	\caption{Adam}\label{alg:Adam}
		\begin{algorithmic}
		\Require{$\alpha, \beta_1, \beta_2, \epsilon, f$}
		\State $m_0 = 0$ -- 1-st moment vector
		\State $v_0 = 0$ -- 2-nd moment vector
		\State $t = 0$ -- timestep

		\While {$\theta$ not converged}
			\State $t = t+1$
			\State $g_t = \nabla_{\theta} f_t(\theta_{t-1})$
			\State $m_t = \beta_1 \cdot m_{t-1} + (1 - \beta_1) \cdot g_t$
			\State $v_t = \beta_2 \cdot v_{t-1} + (1 - \beta_2) \cdot g_t^2$
			\State $\hat{m_t} = \frac{m_t}{1-\beta_1^t}$
			\State $\hat{v_t} = \frac{v_t}{1-\beta_2^t}$
			\State $\theta_t = \theta_{t-1} - \alpha \cdot \frac{\hat{m_t}}{\sqrt{v_t} + \epsilon}$
		\EndWhile
	\end{algorithmic}
	\end{algorithm}

	\begin{algorithm}[H]
	\caption{OASIS}\label{alg:OASIS}
	\begin{algorithmic}
		\Require{$w_0, \eta_0, D_0, \theta_0 = + \infty$}    
		\State $w_1 = w_0 - \eta \hat{D_0}^{-1} \nabla F(w_0)$

		\For{$k = 1, 2, ...$}
		\State $D_k = \beta D_{k-1} + (1-\beta_2) \cdot diag\left( z_k \odot \nabla^2 F(w_k) z_k \right)$
		\State $(\hat{D_k})_{ii} = max \{|D_k|_{i, i} ; \alpha \}$, $\forall i = \overline{1, d}$
		\State $\eta_k = min \{ \sqrt{1 + \theta_{k-1}} \cdot \eta_{k-1}; \frac{||w_k - w_{k-1}||_{\hat{D_k}}}{2 ||\nabla F(w_k) - \nabla F(w_{k-1}) ||_{\hat{D_k}}^* } \}$
		\State $\theta_k = \frac{\eta_k}{\eta_{k-1}}$
		\EndFor

	\end{algorithmic}
\end{algorithm}
\fi

@@

%\section{Headings: first level}
%\label{sec:headings}
% See Section \ref{sec:headings}.
%\subsection{Headings: second level}
%\subsubsection{Headings: third level}
%\paragraph{Paragraph}
%\section{Examples of citations, figures, tables, references}
%\label{sec:others}

\subsection{Citations}

\cite{kingma2014adam}, \cite{jahani2021doubly}, \cite{sadiev2022stochastic}, \cite{beznosikov2022scaled}, \cite{stich2019unified}

%\subsection{Figures}
%See Figure \ref{fig:fig1}. Here is how you add footnotes. \footnote{Sample of the first footnote.}
%\begin{figure}
	%\centering
	%\includegraphics[width=0.5\textwidth]{../figures/log_reg_cs_exp.eps}
	%\caption{Sample figure caption.}
	%\label{fig:fig1}
%\end{figure}

%\subsection{Tables}
%See awesome Table~\ref{tab:table}.
%The documentation for \verb+booktabs+ (`Publication quality tables in LaTeX') is available from:
%\begin{center}
%	%\url{https://www.ctan.org/pkg/booktabs}
%\end{center}

\if 0
\begin{table}
	\caption{Sample table title}
	\centering
	\begin{tabular}{lll}
		\toprule
		\multicolumn{2}{c}{Part}                   \\
		\cmidrule(r){1-2}
		Name     & Description     & Size ($\mu$m) \\
		\midrule
		Dendrite & Input terminal  & $\sim$100     \\
		Axon     & Output terminal & $\sim$10      \\
		Soma     & Cell body       & up to $10^6$  \\
		\bottomrule
	\end{tabular}
	\label{tab:table}
\end{table}
\fi
\if 0
\subsection{Lists}
\begin{itemize}
	\item Lorem ipsum dolor sit amet
	\item consectetur adipiscing elit.
	\item Aliquam dignissim blandit est, in dictum tortor gravida eget. In ac rutrum magna.
\end{itemize}
\fi

>>>>

\title{Methods with preconditioning with weight decay regularization}

\author{ Kreinin M. \\
	Department of Intelligent Systems\\
	MIPT\\
	Moscow, Russia \\
	\texttt{kreinin.mv@phystech.edu} \\
	\And
	Beznosikov A. \\
	Department of Data Science\\
	MIPT\\
	Dolgoprudny, Russia \\
	\texttt{beznosikov.an@phystech.edu} \\
}
\date{}

@@

\keywords{Adam \and OASIS \and Regularization \and ADAHessian \and Weight Decay}

@@

For solving these problems we always scaled adaptive gradients algorithms like ADAM, OASIS, ADAHessian. We investigate how the convergence rate will change when the regularization function is added to these algorithms.

@@

\section{Experiment}
% Мы проведем эксперимент, в котором сравним Adam с добавленной L2 регуляризацией с AdamW, при различных learning rate и decoupled weight, также мы сравним его с измененным алгоритмом AdamW, где регуляризатор занесен под гессиан, также мы сравним его при условии, что теперь минимальное собственное число гессиана, это не epsilon, а гиперпараметр decoupled weight.Проведем те же эксперименты со SGD и L2 регуляризацией и SGD с decoupled weitght при тех же параметрах. Все эксперименты будут проводиться на батчах размера 128, на сетке ResNet18, в 200 эпох. Всё это будет реализовано с помощью библиотеки PyTorch на dataset CIFAR10.

We will conduct an experiment in which we compare Adam with added L2 regularization with AdamW, at different learning rate and decoupled weight, also we will compare it with the modified AdamW algorithm where the regularizer is put under the hessian, also we will compare it under the condition that now the minimal eigenvalue of hessian is not epsilon, but decoupled weight hyperparameter.We will conduct the same experiments with SGD and L2 regularization and SGD with decoupled weitght at the same parameters. All experiments will be performed on batches of size 128, on a ResNet18 grid of 200 epochs. All this will be implemented using the PyTorch library on dataset CIFAR10.
